Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-27 paper.tex
Remove Rich's name.

\author{
  Noel M O'Boyle\correspondingauthor$^1$%
  \email{Noel M O'Boyle\correspondingauthor - baoilleach@gmail.com}
  \and
  Rajarshi Guha$^2$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Egon L Willighagen$^{3}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
  \and
  Samuel E Adams$^4$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^5$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Richard L Apodaca$^{6}$%
  \email{Richard L Apodaca - rapodaca@metamolecular.com}
  \and
  Jean-Claude Bradley$^7$%
  \email{Jean-Claude Bradley - bradlejc@drexel.edu}
  \and
  Igor V Filippov$^8$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Robert M Hanson$^9$%
  \email{Robert M Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{10}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^{11}$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Craig A James$^{12}$%
  \email{Craig A James - cjames@emolecules.com}
  \and
  Nina Jeliazkova$^{13}$%
  \email{Nina Jeliazkova - jeliazkova.nina@gmail.com}
  \and
  Andrew SID Lang$^{14}$%
  \email{Andrew SID Lang - alang@oru.edu}
  \and
  Karol M Langner$^{15}$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  David C Lonie$^{16}$%
  \email{David C Lonie - loniedavid@gmail.com}
  \and
  Daniel M Lowe$^4$%
  \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  J\'{e}r\^{o}me Pansanel$^{17}$%
  \email{J\'{e}r\^{o}me Pansanel - j.pansanel@pansanel.net}
  \and
  Dmitry Pavlov$^{18}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^{5}$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{19}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{20}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{21}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Peter Murray-Rust$^4$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
}

@@

\address{%
    \iid(1)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(2)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA \\
    \iid(3)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden \\
    \iid(4)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(5)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(6)Metamolecular, LLC, 8070 La Jolla Shores Drive \#464, La Jolla, CA 92037, USA \\
    \iid(7)Department of Chemistry, Drexel University, 32nd and Chestnut streets, Philadelphia, PA 19104, USA \\
    \iid(8)Chemical Biology Laboratory, Basic Research Program, SAIC-Frederick,
Inc., NCI-Frederick, Frederick, MD 21702, USA \\
    \iid(9)St. Olaf College, 1520 St. Olaf Ave., Northfield, MN 55057, USA \\
    \iid(10)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(11)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(12)eMolecules Inc., 380 Stevens Ave., Solana Beach, California 92075, USA \\
    \iid(13)Ideaconsult Ltd., 4.A.Kanchev str., Sofia 1000, Bulgaria \\
    \iid(14)Department of Engineering, Computer Science, Physics, and Mathematics, Oral Roberts University, 7777 S. Lewis Ave. Tulsa, OK 74171, USA \\
    \iid(15)Leiden Institute of Chemistry, Leiden University, Einsteinweg 55, 2333 CC Leiden, The Netherlands \\
    \iid(16)Department of Chemistry, State University of New York at Buffalo, Buffalo, NY 14260-3000, USA \\
    \iid(17)Universit\'{e} de Strasbourg, IPHC, CNRS, UMR7178, 23 rue du Loess 67037, Strasbourg, France \\
    \iid(18)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(19)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(20)Department of Chemistry, University of Washington, Seattle, WA 98195, USA \\
    \iid(21)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA 
}%

>>>>

\author{
  Noel M O'Boyle\correspondingauthor$^1$%
  \email{Noel M O'Boyle\correspondingauthor - baoilleach@gmail.com}
  \and
  Rajarshi Guha$^2$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Egon L Willighagen$^{3}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
  \and
  Samuel E Adams$^4$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^5$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Jean-Claude Bradley$^6$%
  \email{Jean-Claude Bradley - bradlejc@drexel.edu}
  \and
  Igor V Filippov$^7$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Robert M Hanson$^8$%
  \email{Robert M Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{9}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^{10}$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Craig A James$^{11}$%
  \email{Craig A James - cjames@emolecules.com}
  \and
  Nina Jeliazkova$^{12}$%
  \email{Nina Jeliazkova - jeliazkova.nina@gmail.com}
  \and
  Andrew SID Lang$^{13}$%
  \email{Andrew SID Lang - alang@oru.edu}
  \and
  Karol M Langner$^{14}$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  David C Lonie$^{15}$%
  \email{David C Lonie - loniedavid@gmail.com}
  \and
  Daniel M Lowe$^4$%
  \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  J\'{e}r\^{o}me Pansanel$^{16}$%
  \email{J\'{e}r\^{o}me Pansanel - j.pansanel@pansanel.net}
  \and
  Dmitry Pavlov$^{17}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^{5}$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{18}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{19}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{20}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Peter Murray-Rust$^4$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
}

@@

\address{%
    \iid(1)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(2)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA \\
    \iid(3)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden \\
    \iid(4)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(5)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(6)Department of Chemistry, Drexel University, 32nd and Chestnut streets, Philadelphia, PA 19104, USA \\
    \iid(7)Chemical Biology Laboratory, Basic Research Program, SAIC-Frederick,
Inc., NCI-Frederick, Frederick, MD 21702, USA \\
    \iid(8)St. Olaf College, 1520 St. Olaf Ave., Northfield, MN 55057, USA \\
    \iid(9)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(10)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(11)eMolecules Inc., 380 Stevens Ave., Solana Beach, California 92075, USA \\
    \iid(12)Ideaconsult Ltd., 4.A.Kanchev str., Sofia 1000, Bulgaria \\
    \iid(13)Department of Engineering, Computer Science, Physics, and Mathematics, Oral Roberts University, 7777 S. Lewis Ave. Tulsa, OK 74171, USA \\
    \iid(14)Leiden Institute of Chemistry, Leiden University, Einsteinweg 55, 2333 CC Leiden, The Netherlands \\
    \iid(15)Department of Chemistry, State University of New York at Buffalo, Buffalo, NY 14260-3000, USA \\
    \iid(16)Universit\'{e} de Strasbourg, IPHC, CNRS, UMR7178, 23 rue du Loess 67037, Strasbourg, France \\
    \iid(17)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(18)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(19)Department of Chemistry, University of Washington, Seattle, WA 98195, USA \\
    \iid(20)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA 
}%
